\chapter{Environmental Requirements}


    \begin{section}{ToolBox for Drawing Diagram}
    A ToolBox will help the student draw the diagram. The student will first select whether he wants to draw a Chen’s Diagram or a Crow’s Foot Diagram. The toolbox will then adjust accordingly, displaying the shapes and edges that are common to the chosen diagram. This will include squares, circles, directed edges, and tick marks (for Crow’s Foot).
    
    \end{section}
    
    \begin{section}{Save Progress of Current Assignment}
    When a student logs in, he/she should be able to start a quiz. As the student progresses through the quiz, the answers answered by the student should be saved in the students personal database. In that way, if he/she wants to stop and continue with the quiz other time, he can do so without starting all over again.
    \end{section}
    
    \begin{section}{List of Available Questions and Their Status}
    While a student is answering questions, there will be a list of all the questions listed horizontally at the top of the page.  Next to each question number will be a small image.  The image will either be a green check mark if the question is answered correctly, a red x is the question is answered incorrectly or a black question mark if the question has not been answered yet.  When the status of the question changes then so will the image next to the question number.
    \end{section}
    
    \begin{section}{Open Space to Draw Diagram}
    After a student selects which question they want to work on a white drawing space will be given to them in which to draw their answer. Off to the side of this space will be the toolbox which they use to do the drawing. There will also be a submit button off to the side somewhere which is what the student is to press when they're finished with their answer.
    \end{section}
    
    \begin{section}{Compatibility With Multiple Browsers}
    The program will open and be usable with all major internet browsers. Including Safari, Chrome, Firefox, Internet Explorer.
    \end{section}





