
\chapter{Safety/Security Requirements}

    \begin{section}{Student Navigates to the Main Page}
        Description: The student reaches the main page of an assignment. \newline
        Primary Actor: Student \newline
        Secondary Actor: Content author \newline
        Steps:
        \begin{enumerate}
            \item{The page loads, displaying the correct questions for the assignment selected.}
            \item{All questions load and display properly.}
            \item{The student response areas load and allow for proper student input.}
        \end{enumerate}
        Successful Post Conditions:
        \begin{itemize}
            \item{The page displayed is for the correct class and assignment.}
            \item{The student gains no access to non-student interfaces.}
            \item{The submission of answers writes only to the students record for the assignment.}
        \end{itemize}
        Exceptional Condition:
        \begin{itemize}
            \item {The student attempts to access a page he/she should not have access to - the student is displayed an appropriate warning message and is not given access to any assignment or interface that he/she is not meant to have access to.}
        \end{itemize}
    \end{section}

    \begin{section}{Professor Navigates to the Main Page}
        Description: The professor reaches the main page of an assignment. \newline
        Primary Actor: Professor \newline
        Secondary Actor: Content author \newline
        Steps:
        \begin{enumerate}
            \item{The page loads, displaying the tools for adding or modifying an assignment and the information corresponding to student-submitted scores.}
            \item{All questions load and display properly.}
            \item{The content-create pallet allows for the full range of content creation.}
            \item{The data corresponding to student submissions accurately reflects the data currently stored for each student.}
        \end{enumerate}
        Successful Post Conditions:
        \begin{itemize}
            \item{The page that is displayed shows the correct class and assignment.}
            \item{The professor is shown the assignment creation and management page.}
            \item{The content changes that are made only apply to the currently selected assignment.}
        \end{itemize}
        Exceptional Condition:
        \begin{itemize}
            \item{The professor attempts to access a page he/she should not have access to - the professor is displayed an appropriate warning message and is not given access to any assignment or interface he/she is not meant to have access to.}
        \end{itemize}
    \end{section}

    \begin{section}{Student Closes Application With Unsaved Answers in the Window}
        Description: The student has entered a response to a question without saving or submitting the assignment. \newline
        Primary Actor: Student \newline
        Secondary Actor: Professor \newline
        Steps:
        \begin{enumerate}
            \item{The student enters a full or partial response to an assignment question.}
            \item{The student does not save or submit the assignment.}
            \item{The student closes the assignment page.}
        \end{enumerate}
        Successful Post Condition:
        \begin{itemize}
            \item{The student is shown a prompt asking if he/she is sure about wanting to leave the page with unsaved responses.}
        \end{itemize}
    \end{section}

    \begin{section}{Student Submits Page with Blank Answers}
        Description: The student submits an assignment with a response that was left blank. \newline
        Primary Actor: Student \newline
        Secondary Actor: Professor \newline
        Steps:
        \begin{enumerate}
            \item{The student accesses the page.}
            \item{The student inputs and saves responses to some questions.}
            \item{The student submits the assignment with some responses that are left entirely blank.}
        \end{enumerate}
        Successful Post Condition:
        \begin{itemize}
            \item{The student is presented with a prompt asking he/she is sure about wanting to submit a blank response to a question.}
        \end{itemize}
    \end{section}

    \begin{section}{Student Submits Assignment That Was Already Submitted}
        Description: After a student submits an assignment, he/she tries to submit the same assignment again. \newline
        Primary Actor: Student \newline
        Secondary Actor: Professor \newline
        Steps:
        \begin{enumerate}
            \item{The student completes an assignment.}
            \item{The student completes the same assignment with different answers.}
            \item{The student submits the assignment again.}
        \end{enumerate}
        Successful Post Condition:
        \begin{itemize}
            \item{The student is presented with a prompt asking if the/she wants to overwrite the submitted assignment - assuming this occurs before the assignment is closed.} 
        \end{itemize}
        Exceptional Condition:
        \begin{itemize}
            \item{If the submission comes after the assignment is closed, the student is informed that the assignment is closed and no subsequent submissions are allowed.} 
        \end{itemize}
    \end{section}
    
    \begin{section}{Student or Professor Tries to Log Into Someone Else’s Account}
        Description: The student or professor tries to log into the  system with the NetID of another student or professor. \newline
        Primary Actors: Student, Professor \newline
        Secondary Actor: System \newline
        Steps:
        \begin{enumerate}
            \item{The student or professor enters someone else’s NetID into the system.}
            \item{The student or professor enters a fake password into the system.}
            \item{The student or professor clicks the “Login” button or the enter key.}
        \end{enumerate}
        Successful Post Conditions:
        \begin{itemize}
            \item{The system prohibits the student or professor from logging into the system with a NetID and password that do not match.}
            \item{The system sends a reply that says that the login was unsuccessful.}
            \item{The system prompts the user to try entering a username and password again.}
        \end{itemize}
    \end{section}
    
    \begin{section}{User (Student/Instructor/Author) Correctly Logs into the Online Tutor System}
        Description: The user logs into the online tutor system by correctly entering his/her netID and password. \newline
        Primary Actor: User \newline
        Precondition: User navigates to the online tutor system’s login web page \newline
        Trigger: User clicks the “Log In” button on the online tutor system’s login web page \newline
        Successful End Condition: The user is successfully logged into his/her account and can see his/her respective homepage on the screen. \newline
        Failed End Condition: The user is brought back to the login web page and is prompted to try logging in again. \newline
        \newline
        Steps:
        \begin{enumerate}
            \item{The user correctly enters his/her netID.}
            \item{The user correctly enters his/her password.}
            \item{The user clicks the “Log In” button.}
        \end{enumerate}
        Exception:
        \begin{itemize}
            \item{The online tutor system does not recognize that the user’s correctly entered netID and password are associated with that user’s existing account.
            The user is brought back to the login web page and is prompted to try logging in again.}
        \end{itemize}
    \end{section}
    
    \begin{section}{User Incorrectly Logs into the Online Tutor System}
        Description: The user logs into the online tutor system by entering an incorrect netID and/or password. \newline
        Primary Actor: User \newline
        Precondition: User navigates to the online tutor system’s login web page \newline
        Trigger: User clicks the “Log In” button on the online tutor system’s login web page \newline
        Successful End Condition: The user is brought back to the login web page and is prompted to try logging in again. \newline
        Failed End Condition: The user is logged into another user’s account and can see that user’s respective homepage on the screen. \newline
        \newline
        Steps:
        \begin{enumerate}
            \item{The user enters an incorrect netID. \newline
	              (and/or)}
            \item{The user enters an incorrect password.}
            \item{The user clicks the “Log In” button.}
        \end{enumerate}
        Exception: None
    \end{section}
    
    \begin{section}{User Correctly Logs out of the Online Tutor System}
        Description: The user is able to successfully log out of the online tutor system. \newline
        Primary Actor: User \newline
        Precondition: User is logged into his/her account \newline 
        Trigger: User clicks the “Log Out” button on one of the online tutor system’s web pages \newline
        Successful End Condition: The user’s screen shows a reply from the online tutor system that says that the log out was successful. \newline
        Failed End Condition: The user’s screen displays the same page that it displayed before the user clicked the “Log Out” button. \newline
        \newline
        Step:
        \begin{enumerate}
            \item{The user clicks the “Log Out” button.}
        \end{enumerate}
        Exception:
        \begin{itemize}
            \item{The “Log Out” button does not have the functionality to successfully log the user out of his/her account.  The user’s screen displays the same page that it displayed before the user clicked the “Log Out” button.}
        \end{itemize}
    \end{section}
    
    \begin{section}{User Creates an Account on the Online Tutor System}
        Description: The user is able to successfully create an account on the online tutor system. \newline
        Primary Actor: User \newline
        Precondition: User navigates to the online tutor system’s login web page \newline
        Trigger: User clicks the “Create” button on the online tutor system’s create acount web page \newline
        Successful End Condition: The user’s screen shows a reply from the system that says that his/her account was 
        successfully created, and the user’s respective homepage is displayed on the screen. \newline
        Failed End Condition: The user receives a reply from the online tutor system that says that the account could not be created. \newline
         \newline
        Steps:
        \begin{enumerate}
            \item{The user clicks the “Create Account” button on the online tutor system’s login web page.}
            \item{The user correctly enters his/her netID.}
            \item{The user correctly enters his/her password.}
            \item{The user clicks the “Create” button.}
        \end{enumerate}
        Exception:
        \begin{itemize}
            \item{The user’s entered netID and/or password is not recognized by the online tutor system as pertaining to an existing student of the respective university or college. 
            The user receives a reply from the online tutor system that says that the account could not be created.}
        \end{itemize}
    
    
    \begin{section}{User Has Unlimited Amount of Attempts to Log In}
        Description: Each user is given a certain (preset) amount of failed login attempts 
        in a given (preset) amount of time to log into the online tutoring system on a particular device.  
        After a user has used up all of his/her failed login attempts on a particular device, 
        that device will be prevented from logging into the system by that user or any other users 
        until a certain (preset) amount of time has passed.  This method is act of security to prevent 
        users from hacking into other users’ accounts.
    \end{section}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




